DLISA: Distributed Learning-based \\ Intelligent Service Agents

### 2014-11-26 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

The advantages of community of web services are that the community facilitates the discovery of web services and a community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs. But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services. The down side to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services because although they have similar functionality, they have different attitudes. When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point. The community coordinator in \emph{community centralized} architecture is responsible for task receive and delivery issues. Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and fires web services, that do not add enough value to the community.

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 1) The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 2) Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

@@

In further detail, DLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in 64 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

We let communities pick the best communities for maximizing their utilities over different time frames. At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$. If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together. Having set $k = 1$ is a very strict and hardly satisfiable condition. In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$. Basically, $k = r \times t$. On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too. However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n) + n.log(n))$.

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{learning rate $\langle r \rangle$, $|N \times N|$ gain matrix $\langle gain \rangle$, community feature vector $\langle CFVS \rangle$}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$r \gets initial learning rate$\;
\While{$i \leq n \land location = 0$}{
  $j \gets 1$\;
  \While{$j < i \land location = 0$}{
    % The "l" before the If makes it so it does not expand to a second line
    \lIf{$a_i = a_j$}{
      $location \gets i$\;
    }
    \lElse{
      $j \gets j + 1$\;
    }
  }
  $i \gets i + 1$\;
}
\Return{location}\;
\caption{{\sc Tree Creation Algorithm}}
\label{algo:duplicate2}
\end{algorithm}

>>>>

The advantages of community of web services are that the community facilitates the discovery of web services and a community provides better quality of services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs. But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services. The down side to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
% because although they have similar functionality, they have different attitudes. 
When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point. The community coordinator in \emph{community centralized} architecture is responsible for task receive and delivery issues. Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services, that do not add enough value to the community.

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 1) The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 2) Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work of sub-communities instead of calculating the complex shapely-value gain distribution method. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

@@

In further detail, DLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

We let communities pick the best communities for maximizing their utilities over different time frames. At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$. If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together. Having set $k = 1$ is a very strict and hardly satisfiable condition. In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$. Basically, $k = 1 + |r \times t|$. On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too. However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $64$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DLISA Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

\subsection{DLISA Tree Creation Complexity}\label{ss:complexity}
Here we analyze the computational complexity of the DLISA decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
